---
title: "Iteration"
author: "jiaying Ning"
date: "11/11/2020"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
set.seed(1)
```

## list

you can put anythingin a list
```{r}
l = list(
vec_numeric = 5:8,
vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE,FALSE),
mat = matrix(1:8, nrow = 2, ncol = 4),
summary = summary(rnorm(100))
)
```

```{r}
l

```
```{r}
# all of these create exact same output
l$vec_numeric
l[[1]]
l[["vec_numeric"]]
mean(l[["vec_numeric"]])

```


# for loop
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(30, 0, 5),
    c = rnorm(40, 10, .2),
    d = rnorm(10, -3, 1)
  )

is.list(list_norms)

```

```{r}
list_norms
```


pause and get the old function

```{r}
library(tibble)
mean_and_sd = function(x){
  
  if(!is.numeric(x)){stop("input must be numeric")}
  if(length(x)<3){
    stop("Input must have at least 3 number")
  }
mean_x=mean(x)
sd_x=sd(x)

tibble(
  mean=mean_x,
  sd=sd_x
)

}
```

I can apply that function to each list of element
```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])

```

# lets use for loop

```{r}
output = vector("list", length = 4) #empty ist with length of 4

output[[1]] = mean_and_sd(list_norms[[1]])

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

output
```


## lets try map!!
```{r}
library(purrr)
output= map(list_norms,mean_and_sd)
output
```

what if you want different function
```{r}
output = map(list_norms,mean)
output
```

can be funciton you wrote, or a embeded function

```{r}
output = map_dbl(list_norms,mean)
output#list as number

```
```{r}
output= map_df(list_norms,mean_and_sd, .id = "input") # keep track of what input are, and put them in column named input
output
```

# List columns!


```{r}
listcol_df = 
  tibble(
    name = c("a","b","c","d"),
    sample = list_norms
  )
```

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(sample)
listcol_df %>% 
  filter (name =="a")
# this is a data frame, but in one column, you have list in that column
# You still can do everything you want to do with dataframe
```

Lets try some operation
```{r}
listcol_df$sample #produce a list
```
```{r}
listcol_df$sample[[1]] #give you the first element of the list
mean_and_sd(listcol_df$sample[[1]])

```

# Can I just map

```{r}
map(listcol_df$sample,mean_and_sd)
#it worked the same!!!
```

if you want to save the output to the same dataframe:
add a list column to the dataframe
```{r}
listcol_df=
listcol_df %>%
  mutate(
    summary = map(sample,mean_and_sd),
    medians = (map_dbl(sample,median)))
```


## weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
get our list columns ...

you want one data frame for each location
```{r}
weather_nest = 
  weather_df %>%
  nest(data = date:tmin) #new column called data
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)
```
```{r}
weather_nest$data[[3]]
```
suppose I want to regree tamx on tmin for each station
```{r}

  lm(tmax ~ tmin, data = weather_nest$data[[1]])
  lm(tmax ~ tmin, data = weather_nest$data[[2]])
  lm(tmax ~ tmin, data = weather_nest$data[[3]])

```

let's write a function
```{r}
weather_lm = function(df) {
    lm(tmax ~ tmin, data = df)

}

output = vector("list",3)

for (i in 1:3){
  output[[i]] = weather_lm(weather_nest$data[[i]])
}



```

what about map
```{r}
map(weather_nest$data,weather_lm)
```
still work

# waht about a map in a list column???

add a column!!!
```{r}
weather_nest =
weather_nest %>%
  mutate(models = map(data,weather_lm))
```

