---
title: "linear model"
author: "jiaying Ning"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(readxl)



knitr::opts_chunk$set(
  fig.width = 6,
    fig.asp = .6,
  out.width = "90%"

)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete =scale_fill_viridis_d
```

```{r}
nyc_airbnb=read_csv("./data/nyc_airbnb.csv")
 
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## fit a model

```{r}
nyc_airbnb %>%
  ggplot(aes(x=stars,y=price, color= borough))+
  geom_point()
```

let's fit linear model
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

```


lets look at result
```{r, include=FALSE}
fit
#function you can do
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)
```

Lets try something better
```{r}
broom::glance(fit) #this is a dataframe
```

```{r}
broom::tidy(fit)
#each borough is comparing is comparing to reference group.
# For stars, for one unit up in stars, with everthing else fixed, we are expecting to see a increase of 31.98 in price
#
```
```{r}
#the beauty of dataframe
#produce table
broom::tidy(fit) %>%
  select(-std.error, -statistic) %>%
  mutate(
    term = str_replace(term,"borough","Borough:")
  ) %>%
  knitr::kable()

```

Nest model, fit models:
fit interaction

```{r}
nyc_airbnb %>% 
  lm(price ~ stars * borough + room_type * borough, data = .) 
```



## be in control of factor

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type))

fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
```
By reorder thee dataset, you are not changing the reference group, because manhattan have most observation


## Diagnostics
```{r}
modelr::add_residuals(nyc_airbnb, fit) %>%
#creating a new column called resid that calculate teh residual according to fitted value
  ggplot(aes(x=borough,y=resid))+
  geom_violin() +
  ylim(-500,1500) #zoom in
```
we see outlier  in Manhattan brooklyn

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point() +
  facet_wrap(. ~borough  )
```

## Hypothesis tests

this give t-test by default
```{r}
fit %>%
  broom::tidy()
```

What about the significance of borough

```{r}
fit_null = lm(price~stars, data = nyc_airbnb)
fit_alt = lm(price~stars + borough, data=nyc_airbnb) 

anova(fit_null,fit_alt) %>%
  broom::tidy()
```

##Nest data, fit models

This is formal and complicated
```{r}
nyc_airbnb %>% 
  lm(price ~ stars * borough + room_type * borough, data = .) %>% 
  broom::tidy() 
#you get main effect and interaction effect
```

This is exploratory but easy to understand
Question: what is the stars effect on different area?
fit different models separatly in each area:
```{r}
#start with nesting everything。nest everything but borogh,given dataset in a nested column,then you fit model to each df
  nyc_airbnb %>% 
  nest(data = -borough) 

```



```{r}
 nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars, data = .x)), #giving lm
    results = map(models, broom::tidy))%>% #tidy lm
  select(-data,-models) %>%
  unnest(results) %>%
  filter(term == "stars")

```

```{r}
 nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)), #giving lm
    results = map(models, broom::tidy))%>% #tidy lm
  select(-data,-models) %>%
  unnest(results) %>%
  filter(term != "(Intercept)") %>%
  select(borough,term,estimate) %>%
  pivot_wider(
    names_from = borough,
    values_from = estimate
  )

#compare interaction
```

Lets nest even more

same question about room type, stars, and we want to take a look into neiborhood
```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan") %>%#only interested in manhattan
    nest(data = -neighborhood) %>% #leave out term neighborhood
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)), #giving lm
    results = map(models, broom::tidy))%>% #tidy lm
  select(-data,-models) %>%
  unnest(results) %>%
  #fit linear models to each neighborhood
  filter(str_detect(term,"room_type")) #whats matter with room type across all of these things
```
```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan") %>%#only interested in manhattan
    nest(data = -neighborhood) %>% #leave out term neighborhood
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)), #giving lm
    results = map(models, broom::tidy))%>% #tidy lm
  select(-data,-models) %>%
  unnest(results) %>%
  #fit linear models to each neighborhood
  filter(str_detect(term,"room_type")) %>% #whats matter with room type across all of these things
  ggplot(aes(x=neighborhood, y=estimate))+
  geom_point()+ 
  facet_wrap(.~term)+
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


