---
title: "simulation"
author: "jiaying Ning"
date: "11/13/2020"
output: html_document
---
```{r}
library(tidyverse)
library(rvest)
```

## lets simulate something

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```



simulate by running:
```{r}
sim_mean_sd(30)
```


suppose we repeat this process, what the distribution of sampele mean and standard deviation will look like


## lets simulate a lot

doing a for loop
```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(n = 30)
}

bind_rows(output) #bind each list into a row, important!!!!
```

ubove do not have a import list 

Lets use a loop funciton
```{r}
?rerun()

sim_result=
rerun(100,sim_mean_sd(n=30)) %>% #same output
  bind_rows()#same output
```


lets look at the result

```{r}
sim_result %>%
  ggplot(aes(x=mu_hat)) +
  geom_density()


sim_result %>%
  ggplot(aes(x=sigma_hat)) +
  geom_density()

```

```{r}
sim_result %>%
  summarize(
    avg_sample_mean = mean(mu_hat),
    sd_samp_mean= sd(mu_hat)
  )
```

## lets try other sample size

```{r}
n_list = 
  list(
    "n_30"  = 30, 
    "n_60"  = 60, 
    "n_120" = 120, 
    "n_240" = 240)

output = vector("list", length = 4)


output[[1]] = rerun(100, sim_mean_sd(n = n_list[[1]])) %>%
  bind_rows()

output[[2]] = rerun(100, sim_mean_sd(n = n_list[[2]])) %>%
  bind_rows()


for (i in 1:4) {
  output[[i]] =  rerun(100, sim_mean_sd(n = n_list[[i]])) %>%
  bind_rows()
}
```



if I want to keep track of everything I have into a data frame
```{r}

sample_results = 
tibble(
  sample_size = c(30,60,120,240)
) %>%
  mutate(
    output_list = map(.x = sample_size,~rerun(1000,sim_mean_sd(.x))), #function inside of a function #rerun a 100 times
    estmate_df = map(output_list, bind_rows)
  )  %>%
  select(-output_list) %>% #i dont want this anymore 
  unnest(estmate_df)


#.x helps you be clear with wjere the element of sample size needs to go infucntion
#the first arguement to go is .x
```



```{r}
sample_results %>%
  mutate(
    sample_size = str_c("n = ", sample_size)
  )%>%
  ggplot(aes(x=sample_size, y=mu_hat)) +
    geom_boxplot()
  
```

the order is not making sense 
```{r}

```


```{r}
sample_results %>%
mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)
  )%>%
  ggplot(aes(x=sample_size, y=mu_hat)) +
    geom_boxplot()
```



```{r}
sample_results %>%
mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)
  )%>%
  ggplot(aes(x=sample_size, y=mu_hat,fill = sample_size)) +
    geom_violin()
```

